comgen-outline

### 2017-06-24 paper/comgen-paper.Rmd
many attempts at bf computation; working bf for prior model comparison; cached temp results

```{r libraries}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "../"
options("scipen"=10) 
```

@@

We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge
We formalize this hypothesis using a simple, Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two distinct components, for example, if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not [@Griffiths2005].
In this task, participants give responses in the form of numbers between 0 and 100 (or, rescaled to be between 0 - 1).
The canonical prior for generating numbers between 0 - 1 is the Beta distribution.

We then assume the data, for each item independently, was generated from one of two distributions: a distribution corresponds to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ as we explicitly posit a left-skewed "transient" distribution.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with some weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \alpha, \beta) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.

We put priors over the latent parameters of this model and infer their credible values by way of Bayesian infernence.

\begin{eqnarray}
\theta & \sim & \text{Uniform}(0, 1) \\
\alpha & \sim & \text{Uniform}(0, 100) \\
\beta & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

To see how well this data-analytic model fits the prevalence prior data, we can use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.

@@

genericEndorsementPriorModel <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

@@

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)

var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  //var a = uniformDrift({a:0, b: 100, width:5});
  //var b = uniformDrift({a:0, b: 100, width:5});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })

  var marginalPrevalence = sample(flip(phi) ? stableComponent : transientComponent)
  return {g, d, phi, marginalPrevalence}
}
'
```

```{r generic-endorsement-priors-model-run, eval = F}
marginal.prevalence <- data.frame()
m.gen.endorse.priors.summary <- data.frame()

for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
  m.gen.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
         model_var = "model", inference_opts = list(method = "MCMC", samples = 1000, burn = 500, verbose = T))

  marginal.prevalence <- bind_rows(marginal.prevalence, 
                                   m.gen.endorse.priors %>% 
                                     filter(Parameter == "marginalPrevalence") %>%
                                     mutate(Property = p))

  m.gen.endorse.priors.summary <- bind_rows(m.gen.endorse.priors.summary,
                                            m.gen.endorse.priors %>% 
                                              mutate(Property = p) %>%
                                              group_by(Property, Parameter) %>%
                                              summarize(MAP = estimate_mode(value),
                                                        cred_upper = hdi_upper(value),
                                                        cred_lower = hdi_lower(value))
                                              )
  #print(p)
}
```

```{r generic-endorsement-priors-figure, eval = F}
ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")
```

The prevalence prior data is indeed structure.

We also see tremendous variability in the shapes of these prevalence distributions.

@@

Having measured the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) in addition to target-category prevalence (e.g., how many robins lay eggs; Expt. 1a), our speaker model (Eq. \ref{eq:S1}) can predict endorsements for the corresponding generic statements (e.g., Robins lay eggs).
To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].

@@

head(d1)
head(d2)

@@

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
This argues against any simple theory that only predicts whether or not a generic statement is true or false. 
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.

To try to understand this endorsement data, we articulate alternative models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.

Our underspecified threshold model has access to the full prior distribution on prevalence $P(h)$, from which it infers likely thresholds for the generic. 
The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
There are thus three unique components of this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
As a control model, we use the same infrastructure but assign the semantics of "Some" to the utterance (i.e., a fixed-threshold which only rules out the lowest possible degree). 
This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
This provides a strict test of our *simple but underspecified* hypothesis.

From the prevalence prior data (Expt. 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*). 
However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $ 20\% < prevalence < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).

<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though a strong version of cue validity has been argued against on *a priori* grounds [@Leslie2007; @Leslie2008].

>>>>

```{r libraries}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

project.path <- "../"
options("scipen"=10) 
```

@@

We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
We formalize this hypothesis using a simple, Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
The "unstructured", alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.

For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with some mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.^[
We use the mean / concentration parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \delta; \beta = (1 - \gamma) \cdot \delta$.
]
The unstructured hypothesis only represents a single component in the prior distribution $P(d) = \text{Beta} (d \mid \gamma, \xi)$.

We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account the flexibility of each model [@LW2014].
We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\theta$):

\begin{eqnarray}
\theta & \sim & \text{Uniform}(0, 1) \\
\gamma & \sim & \text{Uniform}(0, 1) \\
\xi & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property has its own parameters).

@@

genericEndorsementPriorModelHelpers <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

@@

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)
'

structuredPriorModel <- '
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {g, d, phi}
}
'

unstructuredPriorModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  mapData({data: preprocessedResponses}, function(d){
    factor(stableComponent.score(d))
  })
  return {g, d}
}
'
```

```{r generic-endorsement-priors-bayesFactors, eval = F}
genericEndorsementPriorModelPriorLikelihoodHelpers <- '
var properties = _.uniqBy(_.map(data, "Property"));

var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}
'

genericEndorsementPriorModelsPriorLikelihood <- '
var transientComponent = Beta({a:1, b:100})

var model = function(){

  var propertyLogLikes = map(function(property){

    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
    var preprocessedResponses = map(function(d){
        return avoidEndPoints(d / 100)
    }, propertyData);

    var phi = uniformDrift({a:0, b: 1, width:0.2});
    var g = uniformDrift({a:0, b: 1, width:0.2});
    var d = uniformDrift({a:0, b: 100, width:5});
    var stableParams = betaShape({g, d})
    var stableComponent = Beta(stableParams)

    var logLikes = map(function(d){
      var structuredLL = log(
        phi * exp(stableComponent.score(d)) +
        (1 - phi) * exp(transientComponent.score(d))
      )

      var unstructuredLL = stableComponent.score(d);

      return {structuredLL, unstructuredLL}
    }, preprocessedResponses)

    return {
      structuredLL: sum(_.map(logLikes, "structuredLL")), 
      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
    }

  }, properties)

  return {
    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
  }
}
'

```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
marginal.prior.likelihoods <- data.frame()

# 100 samples takes 30s
m.gen.endorse.priors.logLike <- webppl(
    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
          genericEndorsementPriorModelsPriorLikelihood,
          sep = '\n'), 
    data = d.gen.endorse.priors, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "forward", samples = 1000),
    chains = 3, cores = 3
) %>% 
  mutate(value = as.numeric(value))

min.ll.1 <- min(
  m.gen.endorse.priors.logLike$value[
    is.finite(
      m.gen.endorse.priors.logLike$value
      )
    ]
  )

m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
  rowwise() %>%
  mutate(value = ifelse(value == -Inf, min.ll.1, value))

save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
```

```{r generic-endorsement-priors-bayesFactorsLoad}
load(file = '../analysis/generics-priors-loglike.Rdata')
marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
  group_by(Chain, Parameter) %>%
  summarize(mll  = logmeanexp(value))

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
  spread(Parameter, mll) %>%
  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
```
The Bayes Factor indicates the extent to which the data support one model over another.
The overall Bayes Factor in terms of Structured Model (S) over the Unstructured Model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
Indeed, the data strongly suggests the prevalence prior is structured.

It is possible that the data is, in fact, more structured than our simple two-component model. 
To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
We could fit a more complex model to this data (i.e., one with three mixture components); however, we retain the imperfect simpler model for data-analytic ease going forward.

```{r generic-endorsement-priors-savageDickeyModel, eval = F}
savageDickeyModel <-'
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {phi}
}

//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
// var samples = 2000, burn = burn / 2, lag = 0;
var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
verbose: true}, model)
var modelPrior = Infer({method: "forward", samples:10000}, model)

var pointNull = 1;

var logBFs = map(function(diff){
  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
  return [diff, Math.log(savageDickeyRatio)]
}, [0.01, 0.02, 0.03, 0.04, 0.05])

var returnVals = {
  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
}
returnVals
'
```

```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
genericEndorsementPriorSupermodel <- '
var model = function(){
  var alpha = uniformDrift({a:0, b: 1, width:0.2});
  //var structured = flip();
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g1 = uniformDrift({a:0, b: 1, width:0.2});
  var d1 = uniformDrift({a:0, b: 100, width:5});
  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
  // var d0 = uniformDrift({a:0, b: 100, width:5});
  var stableParams1 = betaShape({g: g1, d: d1})//, 
      //stableParams0 = betaShape({g: g0, d: d0});
  var stableComponent1 = Beta(stableParams1)//,
      //stableComponent0 = Beta(stableParams0);

  var transientComponent = Beta({a:1, b:100})
  mapData({data:preprocessedResponses},
    function(d){
    var scr1 = log(phi * exp(stableComponent1.score(d)) +
                    (1 - phi) * exp(transientComponent.score(d)))
    var scr0 = stableComponent1.score(d);
    // display(exp(scr1) + " " + exp(scr0));
    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
    // factor(structured ? scr1 : scr0)
    factor(combined_ll)
  })
  return alpha
}
'
```

```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.supermodel.posterior <- webppl(
    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model",  chains = 2,
                                 cores = 2,
                                 inference_opts = 
                                   list(method = "MCMC",
                                        samples = 2000, 
                                        burn = 2000, 
                                        lag = 2, 
                                        verbose = T)
    )

  qplot(m.gen.endorse.priors.supermodel.posterior$value)
}
```

```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  var logLike = sum(map(function(d){
    var scr = log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    )
    return scr
  }, preprocessedResponses))
  return logLike
}
'
genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d});
  var stableComponent = Beta(stableParams);
  var logLike = sum(map(function(d){
    return stableComponent.score(d)
  }, preprocessedResponses))
  return logLike
}
'
```

```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
marginal.prior.likelihoods <- data.frame()

for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.logLike.enum1 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  m.gen.endorse.priors.logLike.enum0 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)

  marginal.prior.likelihoods <- bind_rows(
    marginal.prior.likelihoods, 
    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
  )
}

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

```{r generic-endorsement-priors-model-run, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 1000
lg = 0
example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )

for (p in example.generics.prior.properties ) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

    m.gen.endorse.priors.structured <- webppl(
      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        isPresent = rbinom(1, 1, prob = phi),
        prevalence = ifelse(isPresent == 1, 
                           rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
                           rbeta(n = 1,
                                 shape1 = 1,
                                 shape2 = 100)),
        Property = p, src = "Structured"
      ) %>% ungroup()

    m.gen.endorse.priors.unstructured <- webppl(
      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        prevalence = rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
        Property = p, src = "Unstructured"
      ) %>% ungroup()

    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
      m.gen.endorse.priors.posteriorPredictive,
      bind_rows(
       m.gen.endorse.priors.structured.predictive %>%
          select( src, Property, prevalence),
      m.gen.endorse.priors.unstructured.predictive %>%
          select( src, Property, prevalence),
      data.frame(Property = p,
                 src = "Data",
                 prevalence = priorData/100)
      )
    )

  # for (c in 1:2){
  #     m.gen.endorse.priors.savage <- webppl(
  #   paste(genericEndorsementPriorModelHelpers, 
  #         savageDickeyModel, sep = '\n'), 
  #   data = priorData, 
  #   data_var = "data"
  #   )

  # m.inferred.prior <- get_samples(
  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
  #     rename(prob = probs), n_samples)
  # 
  # m.inferred.posterior <- get_samples(
  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
  #     rename(prob = probs), n_samples)
  # 
  # posterior.density <- density(m.inferred.posterior$phi,
  #         from = 0, to = 1)
  # 
  # prior.density <- density(m.inferred.prior$phi,
  #         from = 0, to = 1)
  # 
  # logBF01 = log(approxfun(posterior.density)(1)) - 
  #   log(approxfun(prior.density)(1))

  # m.gen.endorse.priors.savage.summary <- bind_rows(
  #   m.gen.endorse.priors.savage.summary,
  #     bind_rows(
  #     data.frame(Property = p, 
  #                Chain = c, 
  #                diff = NA,
  #                logBF01 = logBF01,
  #                BF01= exp(logBF01)),
  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
  #       rename(diff = X1, logBF01 = X2) %>%
  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
  #     )
  # )
  # 
  # }

    #for (c in 1:3){

      # posterior.logspline <-  polspline::logspline(filter(
      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
      #   lbound = 0, ubound = 1)
      # 
      #   posterior <- dlogspline(1, posterior.logspline)
      # prior <- dunif(1, min = 0, max = 1)
      # BF01 <- posterior/prior
      # 
      # print(log(BF01))

  #}

  #print(p)
  #print(priorData)
}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density functions for prior distributions representing the prevalence of eight different features. Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')
    ggplot(m.gen.endorse.priors.posteriorPredictive, 
           aes( x = prevalence, color = src, lty = src))+
      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  coord_fixed()+
    xlab("Prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

```{r generic-endorsement-priors-figure2, eval = F}
ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")
```

@@

In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
This data also includes informaiton about the target-category prevalence (e.g., how many robins lay eggs).
Using the target-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].

@@

@@

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
Such a continuum of judgments is evidence against any theory that only predicts whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.

To try to understand this endorsement data, we articulate a set of simple models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (e.g., prevalence, cue validity) by bootstrapping those data.

Our underspecified threshold model has access to the full prior distribution on prevalence $P(h)$, from which it infers likely thresholds for the generic. 
The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
There are thus three unique components to this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
This provides a strict test of our *simple but underspecified* hypothesis.
